\disstitle

### 2018-06-18 chapters/crosstransf/paper.tex
fix corrupt references
cross domain
fix duplicate label definition

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{crosstransf/cartoon}
  \caption{We learn to predict the ground-image
    segmentation directly from an aerial image of the same location,
  thereby transferring the semantics from the ground to the aerial
image domain.}
	\label{fig:overview}
\end{figure}

@@

	\label{fig:architecture}
\end{figure*}

@@

Our proposed network architecture is composed of four modules. A
convolutional neural network (CNN), $L_a = A(I_a;\Theta_A)$, is used
to extract semantic labels from the aerial imagery. Another CNN,
$S(I_a;\Theta_S)$, uses features extracted from aerial imagery to help 
estimate the transformation matrix, $M = F(x_r, y_r, i_c, j_c,
S(I_a;\Theta_S); \Theta_F)$, based on aerial image features and the
pixel location in the respective images. Finally, we have a
transformation module, $L_{g'}= T(L_a,M)$, that converts from the
aerial viewpoint to the ground-level using the estimated
transformation matrix, $M$. 
There are many choices for these components, and the 
remainder of this section describes the particular choices we made for this 
study. See~\figref{architecture} for a visual overview of the architecture.

@@

We now define the architecture of the transformation estimation neural
network, $F$. The value of the transformation matrix at
location $(r, c)$ is computed through a neural network, $\tilde{F}$,
followed by a {\em softmax} function to normalize the impact of all
pixels sampled from the aerial image:
\begin{align*}
\begin{split}
  M_{rc} &= F\left(r, c, S(I_a; \Theta_S)\right)
  = \frac{e^{\tilde{F}_{r,c}}}{\sum_{c'}{e^{\tilde{F}_{r,c'}}}}, \\
\textrm{where:} ~~~~~&\\
  &\tilde{F}_{r, c} = \tilde{F}\left(i, j, y, x, S(I_a; \Theta_S)\right), 
  ~~\textrm{and}\\
  & i = \lfloor c / w_a \rfloor / h_a, ~~~j = \mathrm{mod}(c,w_a) / w_a, \\
  & y = \lfloor r / w_g \rfloor / h_g, ~~~x = \mathrm{mod}(r,w_g) / w_g.
\label{equ:matmul}
\end{split}
\end{align*}
The base network, $\tilde{F}$, is a multi-layer perceptron, with ReLU
activation functions, that takes as input a 293-element vector.
The network has three layers, with 128, 64 and 1 output channels
respectively (refer to the lower part of~\figref{architecture}).  The
na\"{\i}ve approach can be considered a special case of this
representation where we ignore the aerial image and use a one-hot
encoding representation of rows and columns.

@@

\subsection{Dataset}
\label{sec:dataset}

@@

  \label{fig:dataset}
\end{figure}

We collect our training and testing dataset from the CVUSA
dataset~\cite{workman2015wide}. CVUSA contains approximately 1.5 million
geo-tagged pairs of ground and aerial images from across the
United States. We use the Google Street View panoramas of CVUSA as our
ground images. For each panorama, we also
download an aerial image at zoom level 19 from Microsoft Bing Maps 
in the same location. We filter out panoramas with no available 
corresponding aerial imagery. Using the camera's extrinsic
information, we then warp the panoramas to align with the
aerial images.  We also crop the panoramas vertically 
to reduce the portion of the sky and
ground pixels.  In total, we collected 35,532 image pairs for
training and 8,884 image pairs for testing. Some examples aerial/ground 
image pairs in our dataset are shown \figref{dataset}.

@@

We implemented the proposed architecture using Google's TensorFlow
framework~\cite{abadi2016tensorflow}. We train our networks for 10
epochs with the Adam optimizer~\cite{kingma2014adam}. We enable batch
normalization~\cite{ioffe2015batch} with decay 0.9 in all convolutional and 
fully-connected layers (except for the output layers) to accelerate
the training process. Our implementation is available at \todo{URL withheld 
pending publication}.

@@

\section{Evaluation and Applications}
\label{sec:evaluation}
In this section, we will show that our network architecture can be
used in four different tasks: 1) weakly supervised semantic learning, 
2) aerial imagery labeling, 3) orientation regression and geocalibration, 
and 4) cross-view image synthesis. Additional qualitative results and 
the complete network structure used for cross-view image synthesis 
can be found in our supplemental materials.

@@

We trained our full network architecture (with randomly initialized
weights) to predict ground-level semantic labeling using the dataset
described in \secref{dataset}.  \figref{weakly} shows example output,
$L_a$, from the aerial image understanding CNN. This demonstrates that
the resulting network has learned to extract semantic features from an
aerial image, all without any manual annotated aerial imagery.

@@

\begin{figure}
	\centering
	\includegraphics[width=.8\linewidth]{crosstransf/isprs/precisions}

@@

\begin{table}
  \centering
  \caption{Per-Class Precision on the ISPRS Segmentation Task}
  \begin{tabular}{@{}llcccccc@{}}
    \toprule
    \multirow{2}{*}{Class} & \multirow{2}{*}{Init.} & \multicolumn{5}{c}{Number 
    of training samples} \\
    \cline{3-8}
                   &       & 1 & 2 & 7 & 20 & 54 & 82\\
    \hline
    \multirow{3}{*}{\textbf{\specialcell{Imp.}}}
    & Ours & 0.67 & \textbf{0.74} & \textbf{0.63} & \textbf{0.64} & 0.66 & 
    0.64  \\ 
    & Random & \textbf{0.70} & 0.70 & 0.54 & 0.62 & 0.61 & \textbf{0.73}  \\ 
    & VGG16 & 0.60 & 0.55 & 0.55 & 0.61 & \textbf{0.70} & 0.59  \\ 
    \hline
    \multirow{3}{*}{\textbf{Bldg}} 
    & Ours & 0.72 & \textbf{0.76} & \textbf{0.76} & \textbf{0.80} & 0.75 & 
    \textbf{0.78}  \\ 
    & Random & 0.56 & 0.62 & 0.63 & 0.64 & \textbf{0.82} & 0.71  \\ 
    & VGG16 & \textbf{0.78} & 0.72 & 0.71 & 0.69 & 0.70 & 0.75  \\ 
    \hline
    \multirow{3}{*}{\textbf{\specialcell{Low.}}}
    & Ours & \textbf{0.37} & \textbf{0.43} & \textbf{0.51} & \textbf{0.65} & 
    \textbf{0.67} & \textbf{0.67}  \\ 
    & Random & 0.29 & 0.29 & 0.29 & 0.37 & 0.67 & 0.64  \\ 
    & VGG16 & 0.25 & 0.25 & 0.29 & 0.44 & 0.53 & 0.57  \\ 
    \hline
    \multirow{3}{*}{\textbf{Tree}} 
    & Ours & \textbf{0.68} & \textbf{0.54} & \textbf{0.71} & \textbf{0.71} & 
    \textbf{0.74} & 0.74  \\ 
    & Random & 0.42 & 0.46 & 0.49 & 0.56 & 0.71 & 0.69  \\ 
    & VGG16 & 0.36 & 0.44 & 0.50 & 0.55 & 0.65 & \textbf{0.74}  \\ 
    \hline
    \multirow{3}{*}{\textbf{Car}} 
    & Ours & \textbf{0.13} & \textbf{0.46} & \textbf{0.67} & \textbf{0.48} & 
    \textbf{0.48} & 0.49  \\ 
    & Random & 0.05 & 0.08 & 0.10 & 0.25 & 0.45 & \textbf{0.57}  \\ 
    & VGG16 & 0.05 & 0.11 & 0.20 & 0.20 & 0.25 & 0.23  \\ 
    \bottomrule
    \end{tabular}
  \label{tab:isprs:precisions}
\end{table}

@@

\begin{figure*}
  \setlength{\aheight}{63pt}
  \setlength{\gwidth}{52.44pt}
  \centering

@@

% BingMap
\vspace{5pt}
  \setlength{\aheight}{63pt}
  \setlength{\gwidth}{53.25pt}
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/38_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/57_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/62_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/41_pred}

@@

\begin{figure}
	\centering
	\includegraphics[width=.7\linewidth]{crosstransf/orient/orient_err}
  \caption{Histogram of the orientation errors on the CVUSA dataset.}
	\label{fig:orient:err}
\end{figure}

@@

\item{\textbf{CVUSA:}} We use the test set introduced
in~\secref{dataset} to create this dataset, it has two parts for
orientation estimation and geocalibration, respectively.  For the
orientation regression task, we rotate the aerial image to a random
angle. For the fine-grained geocalibration experiment, we center-crop
the aerial image around a random $x,y$ offset, then rotate the image to a
random angle.  In both experiments, the heading direction of the
ground images are the same. We center crop a 224 $\times$ 448
cutout from each ground image as the query image.

@@

\begin{figure*}
  \setlength{\aheight}{93pt}
  \setlength{\gwidth}{60.65pt}
  \centering
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/186_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/271_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/305_pred}
  \hfill

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=.5\linewidth]{crosstransf/cartoon}
  \caption{We learn to predict the ground-image
    segmentation directly from an aerial image of the same location,
  thereby transferring the semantics from the ground to the aerial
image domain.}
	\label{fig:overview}
\end{figure}

@@

	\label{fig:architecture_cross}
\end{figure*}

@@

Our proposed network architecture is composed of four modules. A
convolutional neural network (CNN), $L_a = A(I_a;\Theta_A)$, is used
to extract semantic labels from the aerial imagery. Another CNN,
$S(I_a;\Theta_S)$, uses features extracted from aerial imagery to help 
estimate the transformation matrix, $M = F(x_r, y_r, i_c, j_c,
S(I_a;\Theta_S); \Theta_F)$, based on aerial image features and the
pixel location in the respective images. Finally, we have a
transformation module, $L_{g'}= T(L_a,M)$, that converts from the
aerial viewpoint to the ground-level using the estimated
transformation matrix, $M$. 
There are many choices for these components, and the 
remainder of this section describes the particular choices we made for this 
study. See~\figref{architecture_cross} for a visual overview of the architecture.

@@

We now define the architecture of the transformation estimation neural
network, $F$. The value of the transformation matrix at
location $(r, c)$ is computed through a neural network, $\tilde{F}$,
followed by a {\em softmax} function to normalize the impact of all
pixels sampled from the aerial image:
\begin{align*}
\begin{split}
  M_{rc} &= F\left(r, c, S(I_a; \Theta_S)\right)
  = \frac{e^{\tilde{F}_{r,c}}}{\sum_{c'}{e^{\tilde{F}_{r,c'}}}}, \\
\textrm{where:} ~~~~~&\\
  &\tilde{F}_{r, c} = \tilde{F}\left(i, j, y, x, S(I_a; \Theta_S)\right), 
  ~~\textrm{and}\\
  & i = \lfloor c / w_a \rfloor / h_a, ~~~j = \mathrm{mod}(c,w_a) / w_a, \\
  & y = \lfloor r / w_g \rfloor / h_g, ~~~x = \mathrm{mod}(r,w_g) / w_g.
\label{equ:matmul}
\end{split}
\end{align*}
The base network, $\tilde{F}$, is a multi-layer perceptron, with ReLU
activation functions, that takes as input a 293-element vector.
The network has three layers, with 128, 64 and 1 output channels
respectively (refer to the lower part of~\figref{architecture_cross}).  The
na\"{\i}ve approach can be considered a special case of this
representation where we ignore the aerial image and use a one-hot
encoding representation of rows and columns.

@@

\subsection{Dataset}
\label{sec:dataset_cross}

@@

  \label{fig:dataset_cross}
\end{figure}

We collect our training and testing dataset from the CVUSA
dataset~\cite{workman2015wide}. CVUSA contains approximately 1.5 million
geo-tagged pairs of ground and aerial images from across the
United States. We use the Google Street View panoramas of CVUSA as our
ground images. For each panorama, we also
download an aerial image at zoom level 19 from Microsoft Bing Maps 
in the same location. We filter out panoramas with no available 
corresponding aerial imagery. Using the camera's extrinsic
information, we then warp the panoramas to align with the
aerial images.  We also crop the panoramas vertically 
to reduce the portion of the sky and
ground pixels.  In total, we collected 35,532 image pairs for
training and 8,884 image pairs for testing. Some examples aerial/ground 
image pairs in our dataset are shown \figref{dataset_cross}.

@@

We implemented the proposed architecture using Google's TensorFlow
framework~\cite{abadi2016tensorflow}. We train our networks for 10
epochs with the Adam optimizer~\cite{kingma2014adam}. We enable batch
normalization~\cite{ioffe2015batch} with decay 0.9 in all convolutional and 
fully-connected layers (except for the output layers) to accelerate
the training process.

@@

\section{Evaluation and Applications}
In this section, we will show that our network architecture can be
used in four different tasks: 1) weakly supervised semantic learning, 
2) aerial imagery labeling, 3) orientation regression and geocalibration, 
and 4) cross-view image synthesis. Additional qualitative results and 
the complete network structure used for cross-view image synthesis 
can be found in our supplemental materials.

@@

We trained our full network architecture (with randomly initialized
weights) to predict ground-level semantic labeling using the dataset
described in \secref{dataset_cross}.  \figref{weakly} shows example output,
$L_a$, from the aerial image understanding CNN. This demonstrates that
the resulting network has learned to extract semantic features from an
aerial image, all without any manual annotated aerial imagery.

@@

\begin{figure}
	\centering
	\includegraphics[width=.7\linewidth]{crosstransf/isprs/precisions}

@@

\begin{table}
  \centering
  \caption{Per-Class Precision on the ISPRS Segmentation Task}
  \begin{tabular}{@{}llcccccc@{}}
    \toprule
    \multirow{2}{*}{Class} & \multirow{2}{*}{Init.} & \multicolumn{5}{c}{Number 
    of training samples} \\
    \cline{3-8}
                   &       & 1 & 2 & 7 & 20 & 54 & 82\\
    \hline
    \multirow{3}{*}{\textbf{\specialcell{Imp.}}}
    & Ours & 0.67 & \textbf{0.74} & \textbf{0.63} & \textbf{0.64} & 0.66 & 
    0.64  \\ 
    & Random & \textbf{0.70} & 0.70 & 0.54 & 0.62 & 0.61 & \textbf{0.73}  \\ 
    & VGG16 & 0.60 & 0.55 & 0.55 & 0.61 & \textbf{0.70} & 0.59  \\ 
    \hline
    \multirow{3}{*}{\textbf{Bldg}} 
    & Ours & 0.72 & \textbf{0.76} & \textbf{0.76} & \textbf{0.80} & 0.75 & 
    \textbf{0.78}  \\ 
    & Random & 0.56 & 0.62 & 0.63 & 0.64 & \textbf{0.82} & 0.71  \\ 
    & VGG16 & \textbf{0.78} & 0.72 & 0.71 & 0.69 & 0.70 & 0.75  \\ 
    \hline
    \multirow{3}{*}{\textbf{\specialcell{Low.}}}
    & Ours & \textbf{0.37} & \textbf{0.43} & \textbf{0.51} & \textbf{0.65} & 
    \textbf{0.67} & \textbf{0.67}  \\ 
    & Random & 0.29 & 0.29 & 0.29 & 0.37 & 0.67 & 0.64  \\ 
    & VGG16 & 0.25 & 0.25 & 0.29 & 0.44 & 0.53 & 0.57  \\ 
    \hline
    \multirow{3}{*}{\textbf{Tree}} 
    & Ours & \textbf{0.68} & \textbf{0.54} & \textbf{0.71} & \textbf{0.71} & 
    \textbf{0.74} & 0.74  \\ 
    & Random & 0.42 & 0.46 & 0.49 & 0.56 & 0.71 & 0.69  \\ 
    & VGG16 & 0.36 & 0.44 & 0.50 & 0.55 & 0.65 & \textbf{0.74}  \\ 
    \hline
    \multirow{3}{*}{\textbf{Car}} 
    & Ours & \textbf{0.13} & \textbf{0.46} & \textbf{0.67} & \textbf{0.48} & 
    \textbf{0.48} & 0.49  \\ 
    & Random & 0.05 & 0.08 & 0.10 & 0.25 & 0.45 & \textbf{0.57}  \\ 
    & VGG16 & 0.05 & 0.11 & 0.20 & 0.20 & 0.25 & 0.23  \\ 
    \bottomrule
    \end{tabular}
  \label{tbl:isprs:precisions}
\end{table}

@@

\begin{figure*}
  \setlength{\aheight}{53.55pt}
  \setlength{\gwidth}{44.574pt}
  \centering

@@

% BingMap
\vspace{5pt}
  \setlength{\aheight}{53.55pt}
  \setlength{\gwidth}{45.2625pt}
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/38_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/57_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/62_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/41_pred}

@@

\begin{figure}
	\centering
	\includegraphics[width=.5\linewidth]{crosstransf/orient/orient_err}
  \caption{Histogram of the orientation errors on the CVUSA dataset.}
	\label{fig:orient:err}
\end{figure}

@@

\item{\textbf{CVUSA:}} We use the test set introduced
in~\secref{dataset_cross} to create this dataset, it has two parts for
orientation estimation and geocalibration, respectively.  For the
orientation regression task, we rotate the aerial image to a random
angle. For the fine-grained geocalibration experiment, we center-crop
the aerial image around a random $x,y$ offset, then rotate the image to a
random angle.  In both experiments, the heading direction of the
ground images are the same. We center crop a 224 $\times$ 448
cutout from each ground image as the query image.

@@

\begin{figure*}
  \setlength{\aheight}{80pt}
  \setlength{\gwidth}{52pt}
  \centering
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/186_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/271_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/305_pred}
  \hfill
